### 2022-01-13 README.Rmd
Imports data.table
pkgdown upgrades
- Navbar now includes articles section with links to data preparation process
- `data-prep` and `dataset` now include 'seealso' section
- Hyperlinks fixed

The data were treated, eliminating any sensitive information that could compromise the identity of the participants or linked individuals.

@@

For more information about the dataset, you can consult the package [documentation](https://nim-ach.github.io/ASQ3/reference/dataset.html).

>>>>

The data were treated, eliminating any sensitive information that could compromise the identity of the participants or linked individuals. Data preparation process can be seen [here](reference/data-prep.html).

@@

For more information about the dataset, you can consult the dataset [documentation](https://nim-ach.github.io/ASQ3/reference/dataset.html).
